Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-13 paper/paper.tex

Instead, we introduce a new algorithm, inspired by a state of the art subgraph isomorphism
algorithm. The approach we discuss requires only $O(\left|\V(P)\right|^2\left|\V(T)\right|)$ space
(this can be thousands of times less than maximum common subgraph approaches, once the constant
factors and orders of $T$ in our instances are considered). We list the algorithm in
\cref{algorithm:sip}, explain it fully in \cref{section:algorithm}, and evaluate it in
\cref{section:evaluation}, but first we will discuss our experimental setup, and then detail some
experiments to verify that we can gain effective domain filtering (\cref{section:degreefiltering})
and implied constraints (\cref{section:pathfiltering}) by using subgraph isomorphism style reasoning
about degrees and paths in the $k$-less setting.

@@

?? Talk about iterating, what to do when a vertex disappears from all target graphs.

@@

What would happen if we used our approach to solve the maximum common induced problem? We could
simply start at $k = 0$, and increase $k$ until a solution is found. This would be tackling the
problem in the opposite direction from existing approaches, which work by attempting to construct
larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: the $k
\downarrow$ is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed in ??.
Bearing in mind the disclaimer in \cref{section:setup} regarding instances not fitting in RAM, we
see that our approach is able to close over twice as many of these instances as the previous state
of the art. (The same conclusion holds even if every instance which is satisfiable with $k = 0$ is
removed from the dataset.)

>>>>

Instead, we introduce a new algorithm, inspired by a state of the art subgraph isomorphism algorithm
\citep{DBLP:conf/cp/McCreeshP15}. The approach we discuss requires only
$O(\left|\V(P)\right|^2\left|\V(T)\right|)$ space (this can be thousands of times less than maximum
    common subgraph approaches, once the constant factors and orders of $T$ in our instances are
considered). We list the algorithm in \cref{algorithm:sip}, explain it fully in
\cref{section:algorithm}, and evaluate it in \cref{section:evaluation}, but first we will discuss
our experimental setup, and then detail some experiments to verify that we can gain effective domain
filtering (\cref{section:degreefiltering}) and implied constraints (\cref{section:pathfiltering}) by
using subgraph isomorphism style reasoning about degrees and paths in the $k$-less setting.

@@

@@

What would happen if we used our approach to solve the maximum common induced problem? We could
simply start at $k = 0$, and increase $k$ until a solution is found. This would be tackling the
problem in the opposite direction from existing approaches, which work by attempting to construct
larger and larger solutions. The dotted lines in \cref{figure:runtimes} show this approach: the $k
\downarrow$ is our algorithm, whilst ``FC'' and ``clique'' are the two algorithms discussed by
\citet{DBLP:conf/cp/McCreeshNPS16}.  Bearing in mind the disclaimer in \cref{section:setup}
regarding instances not fitting in RAM, we see that our approach is able to close over twice as many
of these instances as the previous state of the art. (The same conclusion holds even if every
instance which is satisfiable with $k = 0$ is removed from the dataset.)
